Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.7,
                 alpha = 1,
                 position = position_dodge(width = 4)) + 
    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                   size = 1.7,
                   alpha = 0.1,
                   position = position_dodge(width = 4)) +   
    geom_point(aes(shape = classification)) + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

for (i in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(i, target)] %>%
    dplyr::filter(target_type == "case") %>%
    truth_and_pred_plot() + 
    scale_color_manual(values = colcases) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_pred_plot()  + 
  scale_color_manual(values = coldeaths) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")

>>>>

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df, ttype = "case") {
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                   size = 1.7,
                   alpha = 1,
                   position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(data = unfiltered_data[target_type == ttype], 
               aes(shape = classification)) + 
    geom_line(data = unfiltered_data[target_type == ttype]) + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 7, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

@@

for (i in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(i, target)] %>%
    truth_and_pred_plot(ttype = "case") + 
    scale_color_manual(values = colcases) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
  truth_and_pred_plot(ttype = "death")  + 
  scale_color_manual(values = coldeaths) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")
